---
title: "**Supplementary Figures**"
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output:
  pdf_document:
  latex_engine: xelatex
---

# The carbon footprint and nutrient density of blue foods

Authors: James Robinson, Angus Garrett, Juan Carlos Paredes Esclapez, Eva Maire, Christina Hicks, Nick Graham


\newpage
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.verbose = TRUE)
```

```{r, echo=F} 
## set up figcounter
i = 0
```

```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/final/FigureS1_nutrient_ghg.pdf"); i = i + 1
```

**Fig. S`r i`. Nutritional value and carbon footprint of seafood species** Points are CO2 equivalents per kg of seafood of each species and the corresponding the nutrient density (%). Nutrient density is the summed contribution of a 100g portion to recommended intakes of five nutrients (calcium, iron, selenium, zinc, omega-3 fatty acids) (recommended daily intakes for adults (18-65 years old)).

\newpage

```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/final/FigureS2_UK_profiles_bysector.pdf"); i = i + 1
```

**Fig. S`r i`. Annual production of major seafood products in the UK.** Bars show annual production for UK landings, UK aquaculture, and imported products. Wild species are filled blue, farmed species are filled green.

\newpage

```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/final/FigureS3.pdf"); i = i + 1
```

**Fig. S`r i`. Carbon emissions per nutrient target for all seafood products in the carbon emissions database** Points are the mean kg CO2 per nutrient target for each seafood species, where a nutrient target was the recommended intake (adults 18-65 years old) contained in a 100g portion for 7 nutrients (calcium, iron, selenium, zinc, omega-3 fatty acids, vitamin A). Points are coloured by the number of nutrient targets in a 100g portion. Animal-source foods (beef, chicken, lamb, pork) are included for comparison using CO2 values from (Clune et al., 2017) and nutrient values from (Widdowson, n.d.).







