---
title: "**Supplementary Figures**"
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output:
  pdf_document:
  latex_engine: xelatex
---

# The carbon footprint and nutrient density of blue foods

Authors: James Robinson, Angus Garrett, Juan Carlos Paredes Esclapez, Eva Maire, Christina Hicks, Nick Graham


\newpage
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.verbose = TRUE)
```

```{r, echo=F} 
## set up figcounter
i = 0
```

```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/final/FigureS1_nutrient_ghg.pdf"); i = i + 1
```

**Fig. S`r i`. Nutritional value and carbon footprint of seafood species** Points are kg CO2-eq of each species and its corresponding the nutrient density (%). Nutrient density is the summed contribution of a 100g portion to recommended intakes of five nutrients (calcium, iron, selenium, zinc, omega-3 fatty acids) (recommended daily intakes for adults (18-65 years old)).

\newpage


```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/final/FigureS3.pdf"); i = i + 1
```

**Fig. S`r i`. Carbon emissions per nutrient target for all seafood products in the carbon emissions database** Points are the mean kg CO2-eq per nutrient target for each seafood species, where a nutrient target was the recommended intake (adults 18-65 years old) contained in a 100g portion for 7 nutrients (calcium, iron, selenium, zinc, omega-3 fatty acids, vitamin A). Points are coloured by the number of nutrient targets in a 100g portion. Animal-source foods (beef, chicken, lamb, pork) are included for comparison using CO2 values from (Clune et al., 2017) and nutrient values from (Widdowson, n.d.).

\newpage

```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/final/FigureS2_UK_seafood.pdf"); i = i + 1
```

**Fig. S`r i`. Seafood available for UK consumers.** Points are the estimated UK production (blue, landings and farms) and imported (grey) seafood per year, for all seafood with more than 100 tonnes total production.

\newpage
```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/final/Figure3.pdf"); i = i + 1
```

**Figure S`r i`. Carbon emissions per nutrient target for UK seafood products, for nine essential dietary nutrients.** Points are kg CO2-eq per nutrient target (averaged across species), coloured by the number of nutrient targets in a 100g portion. Targets were recommended intakes for adults (18-65 years old) of nine nutrients (calcium, iron, selenium, zinc, omega-3 fatty acids, vitamins A, D, B12, folate). Animal-source foods (beef, chicken, lamb, pork) are included for comparison using CO2 values from (Clune et al., 2017) and nutrient values from (Widdowson, n.d.).

\newpage
```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/final/FigureSX_UK_fournut_density.pdf"); i = i + 1
```

**Fig. S`r i`. Nutrient density for major UK seafood products estimated for five nutrients (calcium, iron, selenium, zinc, omega-3 fatty acids).** Nutrient density based on recommended daily intakes for adults (18-65 years old), recalculated here for comparison with Fig. 1 (nutrient content of global seafood products).

\newpage
```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/final/FigureSX_GFGscore.pdf"); i = i + 1
```
**Fig. S`r i`. Sustainability and price of UK seafood products.** A) Carbon emissions per nutrient target by sustainability score, where points are the mean sustainability score of each product against the mean kg CO2-eq per nutrient target. B) is the range in sustainability scores by seafood product and C) is the price per kg (Seafish 2021) against kg CO2-eq per nutrient target. Sustainability scores were rescaled such that 0 = low sustainability and 1 = high sustainability, and kg CO2-eq per nutrient target was estimated from recommended intakes of nine nutrients (calcium, iron, selenium, zinc, omega-3 fatty acids, vitamins A, B12, D and folate).

\newpage

```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/final/FigureSX_stock_status.pdf"); i = i + 1
```

**Fig. S`r i`. Pressure and state thresholds for wild fisheries stocks relevant to UK seafood production from 1990-2019.** Bars indicate the proportion of stocks that are underfished (green), overfished (red), or data deficient (unknown), according to estimates of fishing mortality (A, F_MSY_) or spawning stock biomass (B_lim_). Data from CEFAS [REF].